Analysis2

### 2023-11-16 Lahman Analysis/Rough Analysis 2/Analysis2.qmd
Began modeling player's trajectories

```{r}
N_player <- Batting %>% 
  distinct(playerID) %>% 
  pull(playerID) %>% 
  sample(size = 100, replace = FALSE)
```

@@

```{r}
fit28ab <- stan(
  file = "HR28ab.stan",
  data = data28ab,
  iter = 500
)
```

@@

>>>>

```{r}
#Set the seed since the players chosen keep changing
set.seed(300)

N_player <- Batting %>% 
  distinct(playerID) %>% 
  pull(playerID) %>% 
  sample(size = 100, replace = FALSE)
```

@@

```{r}
fit28ab <- stan(
  file = "HR28ab.stan",
  data = data28ab,
  iter = 1000
)
```

@@

### Modeling Player "Trajectories" From Model Prediction

Followed [this vignette](http://mjskay.github.io/tidybayes/articles/tidy-rstanarm.html) from tidybayes.

```{r}
#Start by installing tidybayes

#This shows us what the variables are called in the model (we already know this from the stan code)
get_variables(fit28ab)
```

```{r}
#Grabs the beta1's from the model and shows first 10
fit28ab %>% 
  spread_draws(beta1[group]) %>% 
  head(10)
```

```{r}
#Shows the first 10 beta1's again but also gives medians
fit28ab %>% 
  spread_draws(beta1[group]) %>% 
  median_qi() %>% 
  head(10)
```

```{r}
#Gives us a tidy df of all the outputs from when we print a model fit for a specific parameter
fit28ab %>% 
  spread_draws(beta1[group]) %>% 
  summarise_draws()
```

```{r}
#Though ugly, this output should be replicating the beta1 graph above.
fit28ab %>%
  spread_draws(beta1[group]) %>%
  median_qi(.width = c(.95, .8)) %>%
  ggplot(aes(y = group, x = beta1, xmin = .lower, xmax = .upper)) +
  geom_pointinterval()
```

```{r}
#Note: in the vingette, condition=HR for us and ABC=Samp_Batting
Samp_Batting %>%
  modelr::data_grid(HR) %>%
  add_epred_draws(fit28ab) %>%
  head(10)
```

```{r}
grid = Samp_Batting %>% 
  modelr::data_grid(HR)

means = grid %>% 
  add_epred_draws(fit28ab)
```

I'm getting som errors here, so I'm going to take a break from trying to use tidybayes and give this a go another way.

We takled in the meeting on 11/10 about picking a player who had a lot of seasons so we could see how their trajectory looked over the course of their long career. Selecting arbitrarily, playerID "bayja01" played from 2003-2013. So a nice 11 year long career. (His index is 9)

```{r}
#Grab player 9's estimates for beta0, beta1, and beta2
b0_i9 <- fit28ab %>% 
  spread_draws(beta0[group]) %>% 
  summarise_draws() %>% 
  filter(group == 9)

b1_i9 <- fit28ab %>% 
  spread_draws(beta1[group]) %>% 
  summarise_draws() %>% 
  filter(group == 9)

b2_i9 <- fit28ab %>% 
  spread_draws(beta2[group]) %>% 
  summarise_draws() %>% 
  filter(group == 9)

b0_i9
b1_i9
b2_i9
```

```{r}
#Combine these into one tibble
player_9_est <- b0_i9 %>% 
  bind_rows(b1_i9, b2_i9)
```

```{r}
#We want to plot this guy's fit compared to how he actually did
player_9_Samp_Batting <- Samp_Batting %>% 
  filter(player_index==9) %>% 
  select(playerID, player_index, yearID, Age, AB, HR) %>% 
  mutate(cAge = Age - 30, .after = Age)
  mutate(p = HR / AB) %>% 
  mutate(p_logit = log(p / (1-p)))
```

```{r}
ggplot(data = player_9_Samp_Batting)+ 
  aes(x = cAge, y=p_logit)+
  geom_point()+
  geom_function(fun = function(x) (-2.962388)	+ (-0.0443416*x) + (-0.004696772*(x**2)), color="red")
```

\
\
\
\
